Counting infinitely by Oritatami co-transcriptional folding

### 2019-06-26 paper.tex
intro cont...

%------------------------------------------------------
	\section{Introduction}
%------------------------------------------------------
Our body consists many proteins which is based on genetic sequence in DNA.
DNA sequence has to be copied in order to make proteins because DNA is in cell nucleus.
It is copied to RNA (and its sequence is called \textit{transcript}) by a RNA polymerase and delivered to out of nucleus.
A transcript consists four types nucleobases A, U, G, and C, and a nucleobase are called \textit{bead}
Moreover, they form hydrogen bonds mainly between A and U, and between G and C, then they begin to form at the same time synthesizing.
Once the bead is fixed after that it can not change the position.

>>>>

%------------------------------------------------------
	\section{Introduction}
%------------------------------------------------------
Our body consists many proteins which is based on genetic sequence in DNA.
DNA sequence has to be copied in order to make proteins because DNA is in cell nucleus.
It is copied to RNA (and its sequence is called \textit{transcript}) by a RNA polymerase and delivered to out of nucleus.
A transcript consists four types nucleobases A, U, G, and C, and a nucleobase are called \textit{bead}
Moreover, they form hydrogen bonds mainly between A and U, and between G and C, then they begin to form at the same time synthesizing.
Once the bead is fixed after that it can not change the position.
By repeating this method, transcript form a 3D shape.

A shape of RNA depends on the DNA sequence.
Geary, Rothemund, and Andrsen have succeeded in experimentally making 2D RNA tiles (Fig.\ref{fig:rna_origami}) by repeatedly copying a specific DNA sequence \cite{GearyRothemundAndersen2014}.
Then, Oritatami System was designed as a mathematical model that the process of RNA production and Fig.\ref{fig:origami_on_oritatami} is the 2D RNA tile which is represented on Oritatami System.

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/rna_origami.pdf}
\caption{
A generated and stabilized 2D RNA tile from DNA
}
\label{fig:rna_origami}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/origami_oritatami.pdf}
\caption{
The represented 2D RNA tile on Oritatami System
}
\label{fig:origami_on_oritatami}
\end{figure}
